DraftOne

### 2016-09-08 writing/DraftOne.Rmd
Make bindings visible

>>>>

##Stuff from .R Files

```{r}
sim_df2 <- function(n, central, amp, exposure_type, average_outcome, trend, rr, start.date = "2000-01-01"){
  start.date <- as.Date(start.date)
  date <- seq(from = start.date, by = 1, length.out = n)
  exposure = sim_exposure(n = n, amp = amp, central = central,
                          exposure_type = exposure_type)

  df <- data.frame(date, exposure) %>%
    dplyr:: mutate(outcome = sim_outcome(exposure=exposure, average_outcome=average_outcome, trend = trend,
                                        amp = amp, rr=rr, start.date=start.date))
  return(df)
}
```
